---
title: "BRRR demo"
output:
  html_document:
    df_print: paged
---

## [`BRRR`](https://github.com/brooke-watson/BRRR) by Brook Watson Madubuonwu
 - #### inspired by Rasmus Bååth's [`beepr`](https://github.com/rasmusab/beepr) package
 - #### check out Brook's awesome [blog](https://brooke.science/) for more fun w/R

Install `BRRR`
```{r}
#if(!require(devtools)) {install.packages("devtools")}
#devtools::install_github("brooke-watson/BRRR")

library(BRRR)
```

### `skrrrahh()`
Is the only function in the `BRRR` package

**Argument**:

- `sound` a character string or number specifying what sound to be played by either specifying one of the built in sounds or specifying the path to a wav file. The default is 27. Possible sounds are:
```
## [1] "twochainz"  "twochainz1" "bigboi"     "biggie"    
## [5] "bigsean"    "bigsean1"   "bigsean2"   "bigsean3"  
## [9] "bigsean4"   "bigsean5"   "bigshaq"    "bigshaq1"  
## [13] "birdman"    "birdman1"   "birdman2"   "busta"     
## [17] "chance"     "desiigner"  "diddy"      "drake"     
## [21] "drake1"     "drummaboy"  "fetty"      "flava"     
## [25] "future"     "gucci"      "gucci1"     "gucci2"    
## [29] "jayz"       "jayz1"      "kendrick"   "khaled"    
## [33] "khaled1"    "khaled2"    "khaled3"    "liljon"    
## [37] "liljon1"    "nicki"      "pitbull"    "ross"      
## [41] "ross1"      "schoolboy"  "snoop"      "soulja"    
## [45] "takeoff"    "tpain"      "traviscott" "treysongz" 
## [49] "trick"      "waka"       "weezy"      "yg"   
```
```{r}
# default: gucci saying "BRRR"
skrrrahh()
```
```{r}
# Namesake: 
skrrrahh(11)
```
```{r}
# Play a random rap adlib
skrrrahh(0)
```
```{r}
# use the name
skrrrahh("liljon")
```
```{r}
setwd("~/Desktop/repos/Rladies/BRRR_demo")
# path to a new wave file
# this is from https://soundbible.com
# cat's meow
skrrrahh("wav_files/Cat_Meow.wav")
```

Flava Flav announcing the completion of `slow_function()`
```{r}
# slow_math() is just a function that adds 2 to a number 
# after waiting 1 second
# I found it here: https://cnuge.github.io/post/progress_bar
# input is a number
slow_math = function(x){
  Sys.sleep(1)
  x + 2
}

# slow_function() loops over slow_math()
# the input is a string of numbers
slow_function = function(x){
  
  out= c()
  print("Running slow math on the inputs:")
  
  # progress bar to show that the function is working even though it's slow
  progress_bar = txtProgressBar(min=0, max=length(x), 
                                width = NA, 
                                style = 3, 
                                char="=")
  
  # loop through the provided numbers 
  for(i in 1:length(x)){
    out = c(out , slow_math(x[[i]]))
    #Increase the amount the progress bar is filled by setting the value to i.
    setTxtProgressBar(progress_bar, value = i)
  }
  
  close(progress_bar)
  
  # "Yeaah boi!" when the function is done
  skrrrahh("flava")
  return(out)  
}
```
```{r}
#run the function
slow_function(c(1,2,3))
```

DJ Khaled consoling us when we make an error
```{r}
# Change your options to have DJ Khaled console you everytime you hit an error
# message.
options(error = function() {skrrrahh(34)})
```
```{r eval = F}
# Incorrect implementation of slow_function()
# so we can hear DJ Khaled
slow_function(c(1,2,"b"))
```

## [`beepr`](https://github.com/rasmusab/beepr) for non-rap noises
### `beep()` is the only function

**Arguments**

`sound` character string or number specifying what sound to be played by either specifying one of the built in sounds or specifying the path to a wav file. The default is 1. Possible sounds are:

1) "ping"
2) "coin"
3) "fanfare"
4) "complete"
5) "treasure"
6) "ready"
7) "shotgun"
8) "mario"
9) "wilhelm"
10) "facebook"
11) "sword"

```{r}
# install.packages("beepr")
library(beepr)
beep("coin")
```
```{r}
beep("mario")
```

```{r}
# random beep
beep(0)
```

`slow_function()` with `beepr`
```{r}
# input is a string of numbers
slow_function = function(x){
  
  out= c()
  print("Running slow math on the inputs:")
  
  # progress bar to show that the function is working even though it's slow
  progress_bar = txtProgressBar(min=0, max=length(x), 
                                width = NA, 
                                style = 3, 
                                char="=")
  
  # loop through the provided numbers 
  for(i in 1:length(x)){
    out = c(out , slow_math(x[[i]]))
    #Increase the amount the progress bar is filled by setting the value to i.
    setTxtProgressBar(progress_bar, value = i)
  }
  
  close(progress_bar)
  
  # "Work Complete" when the function is done
  beep(4)
  return(out)  
}
```
```{r}
#run the function
slow_function(c(1,2,3))
```

[Wilhelm scream](https://www.youtube.com/watch?v=W0V-2WdubTs&ab_channel=WatchMojo.com) when there's an error
```{r}
options(error = function() {beep("wilhelm")})
```
```{r eval = F}
# Incorrect implementation of slow_function()
# so we can hear Wilhelm scream
slow_function(c(1,2,"b"))
```



